Extracting The Power of Dependent Types

### 2021-09-24 paper.tex
First attempt on trimming the paper back into 12 pages.
        * removed figure from the intro (for now)
        * removed most of the secion about monad (needs to be
          reintroduced gently)
        * aggressively wrapped figures that are < 2/3 column
        * redefined \paragraph to avoid vertical spacing

@@

\input{latex/intro-example}

@@

This entire paper is a literate Agda script\footnote{The sources of the paper
can be found at \url{https://github.com/ashinkarov/agda-stacklang}.}:
all code is typechecked while generating the paper.

\paragraph{Contributions.}
\begin{itemize}

@@

When dealing with embedded languages that are extracted and run
by external compilers, we are fundamentally bound to have potential
semantic mismatches.  Semantics of the embedding may differ from the
semantics implemented by external compilers, and the translation from the
embedding back to external compilers can also be faulty.  Real world compilers
face exactly the same problem: how do you know that generated assembly
code is doing what you think it is doing?  Addressing such problems
requires fully verified toolchains that run on a verified hardware.
Enormous research efforts are spent towards addressing this
problem~\cite{Leroy09,KumarMNO14}, but this is beyond the scope of this paper.

>>>>

\renewcommand{\paragraph}[1]{\textbf{\textit{#1. }}}

@@

% \input{latex/intro-example}

@@

This entire paper is a \emph{literate Agda} script\footnote{The sources of the paper
can be found at \url{https://github.com/ashinkarov/agda-stacklang}.}:
all code is typechecked while generating the paper.

Our \textit{\textbf{main contributions}} are as follows:

\begin{itemize}

@@

When dealing with embedded languages that are ex\-trac\-ted and run
by external compilers, we are fundamentally bound to have potential
semantic mismatches.  Semantics of the embedding may differ from the
semantics implemented by external compilers, and the translation from the
embedding back to external compilers can also be faulty.  Real world compilers
face exactly the same problem: how do you know that generated assembly
code is doing what you think it is doing?  Addressing such problems
requires fully verified toolchains that run on a verified hardware.
Enormous research efforts are spent towards addressing this
problem~\cite{Leroy09,KumarMNO14}, but this is beyond the scope of this paper.
